Compare pseqs

### 2019-05-27 comparepseqs.Rmd
Remove debug
iDebug

        if ("alpha" %in% names(missing)) {
            alphadiversity <- list(min =  calculateglm(dset, modelstring = fo.alpha.min),
                                   full = calculateglm(dset, modelstring = fo.alpha.full))
            saveRDS(alphadiversity, file = paste0("rds-comparepseqs/alpha-", key , ".rds"))
        }

        if ("bray" %in% names(missing)) {
            bray.dist.matrix <- calculate.beta.matrix(pseq)
            saveRDS(bray.dist.matrix, file = paste0("rds-comparepseqs/bray-", key , ".rds"))
        }

        if ("beta" %in% names(missing)) {        
            betadiversity <- list(min = calculateadonis(dset = dset,
                                                        matrix = bray.dist.matrix,
                                                        covariates = covariates.min,
                                                        npermutations = 1000),
                                  full = calculateadonis(dset = dset,
                                                         matrix = bray.dist.matrix,
                                                         covariates = covariates.full,
                                                         npermutations = 1000))
            saveRDS(betadiversity, file = paste0("rds-comparepseqs/beta-", key , ".rds"))
        }
    }

@@

```{r size}
Reduce(function(...) merge(..., all=T), ret)
```

>>>>

        if ("alpha" %in% names(missing)) {
            message("Missing alpha")
            alphadiversity <- list(min =  calculateglm(dset, modelstring = fo.alpha.min),
                                   full = calculateglm(dset, modelstring = fo.alpha.full))
            saveRDS(alphadiversity, file = paste0("rds-comparepseqs/alpha-", key , ".rds"))
        }

        if ("bray" %in% names(missing)) {
            message("Missing Bray")
            bray.dist.matrix <- calculate.beta.matrix(pseq)
            saveRDS(bray.dist.matrix, file = paste0("rds-comparepseqs/bray-", key , ".rds"))
        }

        if ("beta" %in% names(missing)) {
            message("Missing beta")
            betadiversity <- list(min = calculateadonis(dset = dset,
                                                        matrix = bray.dist.matrix,
                                                        covariates = covariates.min,
                                                        npermutations = 1000),
                                  full = calculateadonis(dset = dset,
                                                         matrix = bray.dist.matrix,
                                                         covariates = covariates.full,
                                                         npermutations = 1000))
            saveRDS(betadiversity, file = paste0("rds-comparepseqs/beta-", key , ".rds"))
        }
    }

@@
